---
title: "Coho qPCR by Coho counts"
author: "Douglas Yu"
date: "24/10/2017"
output: html_document
---

Not yet written correctly for Coho. The input data are not formatted the same as in Sockeye, so it needs 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# add packages that I will use
library(tidyverse) # includes all data-formatting packages as one big package (e.g. ggplot2, tibble, tidyr, readr, purrr, dplyr) # because of conflicts, use:  dplyr::filter, dplyr::lag
library(readxl)
library(knitr)
library(zoo)  # time series R "infrastructure" package
library(cowplot)
library(nlme)
library(MuMIn)
```

```{r coho input}
inputfile <- "data/2016_AukeCoho_qPCR_20171024.xlsx"

coho_qpcr <- read_excel(inputfile, "Sheet1", col_names = TRUE, col_types = c("date","numeric","text","text","text","numeric","text","text","text","numeric","numeric","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip"), na = "NA")

coho_env <- read_excel(inputfile, "Summary", col_names = TRUE, col_types = c("skip","skip","skip","skip","skip","date","numeric","numeric","numeric","numeric","numeric","date","numeric","numeric","numeric","numeric","skip","skip","skip","skip"), na = "NA", n_max = 170)  # check number of rows to be input.  
```


```{r}
names(coho_qpcr)
# [1] "Date"            "orig_order"      "Plate_ID"        "Well"           
# [5] "SampleID"        "SampleNumber"    "SampleReplicate" "CT_omit"        
# [9] "updownstream"    "CT"              "Qty_ng_per_ul"  

names(coho_env)
# [1] "Date"              "Smolts"            "coho_Male"     
# [4] "coho_Female"    "coho_Jack"      "cohoTotalCount"
# [7] "Water_Date"        "Gage_Height"       "Depth_inches"     
# [10] "Q_cfs"             "Avg_Temp"

```
Q_cfs seems to be the measure of flux, aka discharge:  cubic feet per second(?).  Cross sectional area X water velocity

```{r}
# keep ONLY ONE SET of qPCRs per sampleID and remove rows that have no CT value
# coho_qpcr_filtered <- coho_qpcr %>% filter(CT_omit == "no_omit") %>% filter(CT != "NA")

# OR keep ALL SETS of qPCRs per sampleID and remove rows that have no CT value
coho_qpcr_filtered <- coho_qpcr %>% filter(CT != "NA")

coho_qpcr_summary <- coho_qpcr_filtered %>% group_by(SampleID) %>% summarise(Date = first(Date), Plate_ID = first(Plate_ID), SampleNumber = first(SampleNumber), SampleReplicate = first(SampleReplicate), updownstream = first(updownstream), CT_mean = mean(CT, na.rm=TRUE), CT_sd = sd(CT, na.rm=TRUE), Qty_ng_per_ul_mean = mean(Qty_ng_per_ul, na.rm=TRUE), Qty_ng_per_ul_sd = sd(Qty_ng_per_ul, na.rm=TRUE), n_qpcrs = sum(!is.na(CT))) %>% arrange(Date)

# n_qpcrs = n() # previously used instead of n_qpcrs = sum(!is.na(CT))


names(coho_qpcr_summary)
# [1] "Date"               "SampleID"           "Plate_ID"          
# [4] "SampleNumber"       "SampleReplicate"    "updownstream"      
# [7] "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean"
# [10] "Qty_ng_per_ul_sd"   "n_qpcrs"   
 
coho_qpcr_env <-  left_join(coho_qpcr_summary, coho_env, by = "Date")

names(coho_qpcr_env)
#  [1] "SampleID"           "Date"               "Plate_ID"          
#  [4] "SampleNumber"       "SampleReplicate"    "updownstream"      
#  [7] "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean"
# [10] "Qty_ng_per_ul_sd"   "n_qpcrs"            "Smolts"            
# [13] "coho_Male"       "coho_Female"     "coho_Jack"      
# [16] "cohoTotalCount"  "Water_Date"         "Gage_Height"       
# [19] "Depth_inches"       "Q_cfs"              "Avg_Temp"          
# [22] "Q_corr_Qpcr"     

coho_qpcr_env <- coho_qpcr_env %>% mutate(Q_corr_qpcr = Qty_ng_per_ul_mean*(Q_cfs/max(Q_cfs)))

coho_qpcr_env <- coho_qpcr_env %>% mutate(G_corr_qpcr = Qty_ng_per_ul_mean*(Gage_Height/max(Gage_Height)))

coho_qpcr_env_adults <- coho_qpcr_env %>% filter(updownstream == "upstream")

```

At this point, the dataset coho_qpcr_env should have one row per water sample (SampleID). Since there are two water samples per day, there should be an even number of rows (sampling days X 2), but some water samples failed completely in qPCR, so the final number of rows is 243.  The salmon count and water data are thus repeated over the two water samples.  

For graphing, the coho_qpcr_env dataset will need to be separated into two subdatasets (SampleReplicate == A or == B), or do a summarise by SampleNumber, not SampleID.  

```{r}
names(coho_qpcr_env_adults)
#  [1] "SampleID"           "Date"               "Plate_ID"          
#  [4] "SampleNumber"       "SampleReplicate"    "updownstream"      
#  [7] "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean"
# [10] "Qty_ng_per_ul_sd"   "n_qpcrs"            "Smolts"            
# [13] "coho_Male"       "coho_Female"     "coho_Jack"      
# [16] "cohoTotalCount"  "Water_Date"         "Gage_Height"       
# [19] "Depth_inches"       "Q_cfs"              "Avg_Temp"          
# [22] "Q_corr_Qpcr"        "G_corr_Qpcr"    

# only analyse sampleReplicate A or B
coho_qpcr_env_adults_A <- coho_qpcr_env_adults %>% filter(SampleReplicate == "A")
coho_qpcr_env_adults_B <- coho_qpcr_env_adults %>% filter(SampleReplicate == "B")

coho_qpcr_env_adults_use <- coho_qpcr_env_adults_B

sockadults <- ggplot(coho_qpcr_env_adults_use, aes(Date, cohoTotalCount)) + geom_line() + xlab("") + ylab("Adult Counts") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

sockqpcrcorrQ <- ggplot(coho_qpcr_env_adults_use, aes(Date, Q_corr_qpcr)) + geom_line() + xlab("") + ylab("Qcfs_corr_qPCR") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

sockqpcr <- ggplot(coho_qpcr_env_adults_use, aes(Date, Qty_ng_per_ul_mean)) + geom_line() + xlab("") + ylab("qPCR conc") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

Q_cfs <- ggplot(coho_qpcr_env_adults_use, aes(Date, Q_cfs)) + geom_line() + xlab("") + ylab("Q_cfs") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")
water <- ggplot(coho_qpcr_env_adults_use, aes(Date, Gage_Height)) + geom_line() + xlab("") + ylab("Gage Height") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")
sockqpcrcorrG <- ggplot(coho_qpcr_env_adults_use, aes(Date, G_corr_qpcr)) + geom_line() + xlab("") + ylab("Gage_corr_qPCR") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")
temp <- ggplot(coho_qpcr_env_adults_use, aes(Date, Avg_Temp)) + geom_line() + xlab("") + ylab("Avg Temp") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

plot_grid(sockadults, sockqpcr, sockqpcrcorrQ, Q_cfs, sockqpcrcorrG, water, temp, nrow = 7, align = "v")


# background_grid(major = c("xy", "x", "y", "only_minor", "none"), minor = c("xy", "x", "y", "none"), size.major = 0.2, size.minor = 0.5, colour.major = "grey90", colour.minor = "grey98")
```

http://ggplot2.tidyverse.org/reference/facet_grid.html
https://cran.r-project.org/web/packages/cowplot/vignettes/introduction.html

```{r}
# write.csv(coho_qpcr_env_adults_A, "analysis/coho_qpcr_env_adults_A.csv")
# write.csv(coho_qpcr_env_adults_B, "analysis/coho_qpcr_env_adults_B.csv")
names(coho_qpcr_env_adults_use)
```

```{r}
coho_qpcr_env_adults_use <- coho_qpcr_env_adults_use %>% filter(SampleNumber <= 70) # remove samples after the main coho run has gone, to avoid qPCR reactions with dead coho adults
with(coho_qpcr_env_adults_use, plot(cohoTotalCount, Qty_ng_per_ul_mean))
with(coho_qpcr_env_adults_use, plot(cohoTotalCount, Q_corr_qpcr))
mdl1 <- lm(cohoTotalCount ~ Q_corr_qpcr, data=coho_qpcr_env_adults_use)
summary(mdl1)
par(mfrow=c(2,2))
plot(mdl1)
par(mfrow=c(1,1))
```

```{r}
plot(residuals(mdl1), type="b")
abline(h=0, lty=3)
```

```{r}
acf(residuals(mdl1))
```

```{r}
mdl1.ac <- gls(cohoTotalCount ~ Q_corr_qpcr, data=coho_qpcr_env_adults_use, 
              correlation = corAR1(form=~Q_corr_qpcr),
              na.action=na.omit)
summary(mdl1.ac)
```

```{r}
coef(mdl1)
coef(mdl1.ac)
qqnorm(mdl1.ac)
```

```{r}
acf(residuals(mdl1.ac, type="p"))
```

```{r}
model.sel(mdl1, mdl1.ac)
```



Tutorial on how to analyse time series
https://rpubs.com/markpayne/164550

```{r}
dat.raw <- read.table("data/Hawaii.txt",header=TRUE)
dat.all <- data.frame(year=dat.raw$Year,birds=sqrt(dat.raw$Moorhen.Kauai),rain=dat.raw$Rainfall)
dat <- subset(dat.all,year>=1973)
# save(dat, file="Correlation_data.RData")
```

```{r}
plot(dat$year, dat$birds)
```

```{r}
mdl <- lm(birds ~ year, data=dat)
summary(mdl)
par(mfrow=c(2,2))
plot(mdl)
```

```{r}
par(mfrow=c(1,1))
plot(residuals(mdl))
```

```{r}
plot(residuals(mdl),type="b")
abline(h=0,lty=3)
```

```{r}
acf(residuals(mdl))
```

```{r}
library(nlme)
mdl.ac <- gls(birds ~ year, data=dat, 
              correlation = corAR1(form=~year),
              na.action=na.omit)
summary(mdl.ac)
```

```{r}
coef(mdl)
```

```{r}
coef(mdl.ac)
```

```{r}
plot(fitted(mdl.ac), residuals(mdl.ac))
abline(h=0,lty=3)
```

```{r}
qqnorm(mdl.ac)
```

```{r}
acf(residuals(mdl.ac,type="p"))
```

```{r}
model.sel(mdl, mdl.ac)
```


```{r}
ccf() # used to calculate cross-correlation of two univariate time series
```

https://onlinecourses.science.psu.edu/stat510/node/75/
https://stats.stackexchange.com/questions/29096/correlation-between-two-time-series
https://svds.com/avoiding-common-mistakes-with-time-series/



Don't run this code. 
Set up github remote on https://github.com/dougwyu/2017_2016_Auke_qPCR
https://www.r-bloggers.com/rstudio-and-github/
Open Terminal
```{bash, }
git remote add origin https://github.com/dougwyu/2017_2016_Auke_qPCR.git
git config remote.origin.url git@github.com:dougwyu/2017_2016_Auke_qPCR.git
git pull -u origin master
git push -u origin master
```
Pull and Push buttons are now active
https://github.com/dougwyu/2017_2016_Auke_qPCR


INLA
IRW2 time series autocorrelations, used in the same way as other inla autocorrelation models f(IRW2 )
vienna and inla time series 

