# Salmon Project

Li Yuanheng, 12 Dec 2017
last modified Apr 11 2018

Frequentist version of the model and truncating the model to exclude dead-fish DNA

DY questions:
1.  what is the source of Qty_ng_per_ul_mean?  I can't find these numbers in AukeCreek_Sockeye_2016_qPCRVsCount_20170802.2.xlsx
2.  what is source of Q_corr_qpcr.rm?


```{r, eval = FALSE}
rm(list=ls())
```

```{r packages and functions}
lapply(c('zoo','cowplot','nlme','MuMIn','readxl','sp','geoR','lubridate','tidyverse','INLA'),library,character.only = T)
# geoR requires XQuartz to be installed, from xquartz.macosforge.org
# install.packages("INLA", repos="https://inla.r-inla-download.org/R/stable", dep=TRUE)
```

```{r}
sessionInfo()
source('source_salmon.r')
```


```{r sockeye input}
inputfile <- "data/AukeCreek_Sockeye_2016_qPCRVsCount_20170802.2.xlsx"

sockeye_qpcr <- read_excel(inputfile, "Ct_Sockeye_2016_work", col_names = TRUE, col_types = c("date","numeric","text","text","text","numeric","text","text","text","numeric","numeric","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip","skip"), na = "NA")

sockeye_env <- read_excel(inputfile, "Summary", col_names = TRUE, col_types = c("skip","skip","skip","skip","skip","date","numeric","numeric","numeric","numeric","numeric","date","numeric","numeric","numeric","numeric","skip","skip","skip","skip"), na = "NA", n_max = 170)  # check number of rows to be input.  
```


```{r names}
names(sockeye_qpcr)
# [1] "Date"            "orig_order"      "Plate_ID"        "Well"           
# [5] "SampleID"        "SampleNumber"    "SampleReplicate" "CT_omit"        
# [9] "updownstream"    "CT"              "Qty_ng_per_ul"  

names(sockeye_env)
# [1] "Date"              "Smolts"            "Sockeye_Male"     
# [4] "Sockeye_Female"    "Sockeye_Jack"      "SockeyeTotalCount"
# [7] "Water_Date"        "Gage_Height"       "Depth_inches"     
# [10] "Q_cfs"             "Avg_Temp"

```
Q_cfs seems to be the measure of flux, aka discharge:  cubic feet per second(?).  Cross sectional area X water velocity

```{r summarise}
# keep ONLY ONE SET of qPCRs per sampleID and remove rows that have no CT value
# sockeye_qpcr_filtered <- sockeye_qpcr %>% filter(CT_omit == "no_omit") %>% filter(CT != "NA")

# OR keep ALL SETS of qPCRs per sampleID and remove rows that have no CT value
sockeye_qpcr_filtered <- sockeye_qpcr %>% filter(CT != "NA")

sockeye_qpcr_summary <- sockeye_qpcr_filtered %>% group_by(SampleID) %>% summarise(Date = first(Date), Plate_ID = first(Plate_ID), SampleNumber = first(SampleNumber), SampleReplicate = first(SampleReplicate), updownstream = first(updownstream), CT_mean = mean(CT, na.rm=TRUE), CT_sd = sd(CT, na.rm=TRUE), Qty_ng_per_ul_mean = mean(Qty_ng_per_ul, na.rm=TRUE), Qty_ng_per_ul_sd = sd(Qty_ng_per_ul, na.rm=TRUE), n_qpcrs = sum(!is.na(CT))) %>% arrange(Date)

# n_qpcrs = n() # previously used instead of n_qpcrs = sum(!is.na(CT))

names(sockeye_qpcr_summary)
#  [1] "SampleID"           "Date"               "Plate_ID"           "SampleNumber"       "SampleReplicate"   
#  [6] "updownstream"       "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean" "Qty_ng_per_ul_sd"  
# [11] "n_qpcrs"           
 
sockeye_qpcr_env <-  left_join(sockeye_qpcr_summary, sockeye_env, by = "Date")

names(sockeye_qpcr_env)
#  [1] "SampleID"           "Date"               "Plate_ID"           "SampleNumber"       "SampleReplicate"   
#  [6] "updownstream"       "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean" "Qty_ng_per_ul_sd"  
# [11] "n_qpcrs"            "Smolts"             "Sockeye_Male"       "Sockeye_Female"     "Sockeye_Jack"      
# [16] "SockeyeTotalCount"  "Water_Date"         "Gage_Height"        "Depth_inches"       "Q_cfs"             
# [21] "Avg_Temp"        

# sockeye_qpcr_env <- sockeye_qpcr_env %>% mutate(Q_corr_qpcr = Qty_ng_per_ul_mean*(Q_cfs/max(Q_cfs)))
# qPCR DNA concentration (ng/ul) * water volume (flux cubic feet per second) == total DNA
sockeye_qpcr_env <- sockeye_qpcr_env %>% mutate(Q_corr_qpcr = Qty_ng_per_ul_mean*Q_cfs) 

# sockeye_qpcr_env <- sockeye_qpcr_env %>% mutate(G_corr_qpcr = Qty_ng_per_ul_mean*(Gage_Height/max(Gage_Height)))
# qPCR DNA concentration (ng/ul) * water height (gage height) == total DNA
sockeye_qpcr_env <- sockeye_qpcr_env %>% mutate(G_corr_qpcr = Qty_ng_per_ul_mean*Gage_Height)

sockeye_qpcr_env_adults <- sockeye_qpcr_env %>% filter(updownstream == "upstream")
```

At this point, the dataset sockeye_qpcr_env should have one row per water sample (SampleID). Since there are two water samples per day, there should be an even number of rows (sampling days X 2), but some water samples failed completely in qPCR, so the final number of rows is 243.  The salmon count and water data are thus repeated over the two water samples.  

For graphing, the sockeye_qpcr_env dataset will need to be separated into two subdatasets (SampleReplicate == A or == B), or do a summarise by SampleNumber, not SampleID.  

```{r choose A or B replicate}
names(sockeye_qpcr_env_adults)
#  [1] "SampleID"           "Date"               "Plate_ID"           "SampleNumber"       "SampleReplicate"   
#  [6] "updownstream"       "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean" "Qty_ng_per_ul_sd"  
# [11] "n_qpcrs"            "Smolts"             "Sockeye_Male"       "Sockeye_Female"     "Sockeye_Jack"      
# [16] "SockeyeTotalCount"  "Water_Date"         "Gage_Height"        "Depth_inches"       "Q_cfs"             
# [21] "Avg_Temp"           "Q_corr_qpcr"        "G_corr_qpcr"           

# only analyse sampleReplicate A or B
sockeye_qpcr_env_adults_A <- sockeye_qpcr_env_adults %>% filter(SampleReplicate == "A")
sockeye_qpcr_env_adults_B <- sockeye_qpcr_env_adults %>% filter(SampleReplicate == "B")

sockeye_qpcr_env_adults_use <- sockeye_qpcr_env_adults_B
```

```{r ggplot timelines}

sockadults <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, SockeyeTotalCount)) + geom_line() + xlab("") + ylab("Adult Counts") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

sockqpcrcorrQ <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, Q_corr_qpcr)) + geom_line() + xlab("") + ylab("Qcfs_corr_qPCR") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

sockqpcr <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, Qty_ng_per_ul_mean)) + geom_line() + xlab("") + ylab("qPCR conc") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

Q_cfs <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, Q_cfs)) + geom_line() + xlab("") + ylab("Q_cfs") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

water <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, Gage_Height)) + geom_line() + xlab("") + ylab("Gage Height") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

sockqpcrcorrG <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, G_corr_qpcr)) + geom_line() + xlab("") + ylab("Gage_corr_qPCR") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

temp <- ggplot(sockeye_qpcr_env_adults_use, aes(Date, Avg_Temp)) + geom_line() + xlab("") + ylab("Avg Temp") + background_grid(major = "x", minor="x", size.minor = 0.5, colour.minor = "grey90")

plot_grid(sockadults, sockqpcr, sockqpcrcorrQ, Q_cfs, sockqpcrcorrG, water, temp, nrow = 7, align = "v")


# background_grid(major = c("xy", "x", "y", "only_minor", "none"), minor = c("xy", "x", "y", "none"), size.major = 0.2, size.minor = 0.5, colour.major = "grey90", colour.minor = "grey98")
```

http://ggplot2.tidyverse.org/reference/facet_grid.html
https://cran.r-project.org/web/packages/cowplot/vignettes/introduction.html

```{r}
# write.tsv(sockeye_qpcr_env_adults_A, "analysis/sockeye_qpcr_env_adults_A.tsv")
# write.tsv(sockeye_qpcr_env_adults_B, "analysis/sockeye_qpcr_env_adults_B.tsv")

# sockeye_qpcr_env_adults_use <- read_tsv("analysis/sockeye_qpcr_env_adults_B.tsv")
```

```{r lag and lead Q_corr_qpcr}
# create lead and lag variables of qPCR*Q_cfs to test for temporal autocorrelation
sockeye_qpcr_env_adults_use <- sockeye_qpcr_env_adults_use %>% dplyr::mutate(Q_corr_qpcr.lag = lag(Q_corr_qpcr))
sockeye_qpcr_env_adults_use <- sockeye_qpcr_env_adults_use %>% dplyr::mutate(Q_corr_qpcr.lead = lead(Q_corr_qpcr))

names(sockeye_qpcr_env_adults_use)
#  [1] "SampleID"           "Date"               "Plate_ID"           "SampleNumber"       "SampleReplicate"   
#  [6] "updownstream"       "CT_mean"            "CT_sd"              "Qty_ng_per_ul_mean" "Qty_ng_per_ul_sd"  
# [11] "n_qpcrs"            "Smolts"             "Sockeye_Male"       "Sockeye_Female"     "Sockeye_Jack"      
# [16] "SockeyeTotalCount"  "Water_Date"         "Gage_Height"        "Depth_inches"       "Q_cfs"             
# [21] "Avg_Temp"           "Q_corr_qpcr"        "G_corr_qpcr"        "Q_corr_qpcr.lag"    "Q_corr_qpcr.lead"  
```


```{r read in data see salmon_datamining.r, eval = FALSE}
dd.qpcr.env.adults.rm <- sockeye_qpcr_env_adults_use
# the code below uses dd.qpcr.env.adults.rm as the input dataset, but the code above produces sockeye_qpcr_env_adults_use as the dataset, so this links between the two 

# dd.qpcr.env.adults.rm = read.table(file='data/sockeye_adults_narm_B.csv',sep=',',header=T)
# there's another file where NAs of qPCR are treated as zero ->
# file='data/sockeye_adults_nazero_B.csv'
# the plots I sent to you before are results of this dataset
```

```{r format dates}
dd.qpcr.env.adults.rm$Date = as.POSIXct(dd.qpcr.env.adults.rm$Date, format='%Y-%m-%d')
dd.qpcr.env.adults.rm$Water_Date = as.POSIXct(dd.qpcr.env.adults.rm$Water_Date, format='%Y-%m-%d')
	
dd.qpcr.env.adults.rm$txtdate = strptime(as.character(dd.qpcr.env.adults.rm$Date),'%Y-%m-%d')
dd.qpcr.env.adults.rm$txtdate = as.factor(format(dd.qpcr.env.adults.rm$txtdate,'%m-%d'))
	
datex=as.Date(strptime(dd.qpcr.env.adults.rm$txtdate,'%m-%d')) # vector of number of days since day 0 for each sample (row)
a = c(0,int_diff(datex)/days(1))
for (i in length(a):1){	
    a[i]=sum(a[1:i]) 
    }
dd.qpcr.env.adults.rm$date.n = a
```

```{r truncate to remove DNA from dead adults and eggs/sperm}
dd.qpcr.env.adults.rm <- dd.qpcr.env.adults.rm %>% dplyr::filter(SampleNumber < 45)
```

```{r standardize variable}
dd.qpcr.env.adults.rm$Q_corr_qpcr.norm2 = MyStd(dd.qpcr.env.adults.rm$Q_corr_qpcr) # dd.qpcr.env.adults.rm$Q_corr_qpcr.rm = Qty_ng_per_ul_mean/Q_cfs, standardised
hist(dd.qpcr.env.adults.rm$Q_corr_qpcr.norm2, breaks=10)

# dd.qpcr.env.adults.rm$testQq <- dd.qpcr.env.adults.rm$Qty_ng_per_ul_mean*dd.qpcr.env.adults.rm$Q_cfs
# dd.qpcr.env.adults.rm$testq_overQ <- dd.qpcr.env.adults.rm$Qty_ng_per_ul_mean/dd.qpcr.env.adults.rm$Q_cfs
```

```{r cut to regularly spaced time-series}
a
a[2:110]
a[1:109]
a[2:110]-a[1:109]
a

dd.qpcr.env.adults.rm = dd.qpcr.env.adults.rm[7:43, ]
dd.qpcr.env.adults.rm$txtdate
```

```{r sockeye count as response and Q_corr_qpcr as predictor}
par(mfrow=c(1,1))
# Poisson model
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr*Avg_Temp,data=dd.qpcr.env.adults.rm,family="poisson")
summary(flowDNAvsCount)
# very overdispersed and interaction ns
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr + Avg_Temp,data=dd.qpcr.env.adults.rm,family="poisson")
summary(flowDNAvsCount)
# very overdispersed
# quasipoisson
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr+Avg_Temp,data=dd.qpcr.env.adults.rm,family="quasipoisson")
summary(flowDNAvsCount)

plot(dd.qpcr.env.adults.rm$Date,dd.qpcr.env.adults.rm$SockeyeTotalCount,type='l', ylim=c(0, 900), main = "Q_corr_qpcr")
lines(dd.qpcr.env.adults.rm$Date[1:37],exp(predict(flowDNAvsCount)),lty=2,col="black")
lines(dd.qpcr.env.adults.rm$Date[1:37],dd.qpcr.env.adults.rm$Q_cfs[1:37],lty=3,col="blue")
lines(dd.qpcr.env.adults.rm$Date[1:37],10*dd.qpcr.env.adults.rm$Avg_Temp[1:37],lty=3,col="red")

acf(resid(flowDNAvsCount))
# residuals are not autocorrelated
# 
dd.qpcr.env.adults.rm$SockeyeTotalCount
sum(dd.qpcr.env.adults.rm$SockeyeTotalCount)
exp(predict(flowDNAvsCount))
sum(exp(predict(flowDNAvsCount)))
```

```{r sockeye count as response and Q_corr_qpcr.lag as predictor}
# Q_corr_qpcr.lag means that yesterday's qPCR measure is used to predict today's salmon count
# Poisson model
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lag * Avg_Temp,data=dd.qpcr.env.adults.rm,family="poisson")
summary(flowDNAvsCount)
# very overdispersed and interaction sig
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lag * Avg_Temp,data=dd.qpcr.env.adults.rm,family="quasipoisson")
summary(flowDNAvsCount)
# quasipoisson and all terms non sig
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lag + Avg_Temp,data=dd.qpcr.env.adults.rm,family="quasipoisson")
summary(flowDNAvsCount)

par(mfrow=c(1,1))
plot(dd.qpcr.env.adults.rm$Date,dd.qpcr.env.adults.rm$SockeyeTotalCount,type='l')
lines(dd.qpcr.env.adults.rm$Date[1:37],exp(predict(flowDNAvsCount)),lty=2,col="black")
lines(dd.qpcr.env.adults.rm$Date[1:37],dd.qpcr.env.adults.rm$Q_cfs[1:37],lty=3,col="blue")
lines(dd.qpcr.env.adults.rm$Date[1:37],10*dd.qpcr.env.adults.rm$Avg_Temp[1:37],lty=3,col="red")

acf(resid(flowDNAvsCount))
# residuals are not autocorrelated

```

```{r sockeye count as response and Q_corr_qpcr.lead as predictor}
# Q_corr_qpcr.lag means that tomorrow's qPCR measure is used to predict today's salmon count
# Poisson model
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lead * Avg_Temp,data=dd.qpcr.env.adults.rm,family="poisson")
summary(flowDNAvsCount)
# very overdispersed and interaction sig
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lead * Avg_Temp,data=dd.qpcr.env.adults.rm,family="quasipoisson")
summary(flowDNAvsCount)
# quasipoisson and all terms non sig
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr.lead + Avg_Temp,data=dd.qpcr.env.adults.rm,family="quasipoisson")
summary(flowDNAvsCount)
# quasipoisson and both main terms sig

par(mfrow=c(1,1))
plot(dd.qpcr.env.adults.rm$Date,dd.qpcr.env.adults.rm$SockeyeTotalCount,type='l')
lines(dd.qpcr.env.adults.rm$Date[1:37],exp(predict(flowDNAvsCount)),lty=2,col="black")
lines(dd.qpcr.env.adults.rm$Date[1:37],dd.qpcr.env.adults.rm$Q_cfs[1:37],lty=3,col="blue")
lines(dd.qpcr.env.adults.rm$Date[1:37],10*dd.qpcr.env.adults.rm$Avg_Temp[1:37],lty=3,col="red")

acf(resid(flowDNAvsCount))
# residuals are not autocorrelated

```

```{r sockeye count as response and Q_corr_qpcr + Q_corr_qpcr.lead as predictor}
# Q_corr_qpcr.lag means that tomorrow's qPCR measure is used to predict today's salmon count
# Poisson model
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr + Q_corr_qpcr.lead + Avg_Temp,data=dd.qpcr.env.adults.rm,family="poisson")
summary(flowDNAvsCount)
# very overdispersed
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr*Avg_Temp + Q_corr_qpcr.lead*Avg_Temp,data=dd.qpcr.env.adults.rm, family="quasipoisson")
summary(flowDNAvsCount)
# quasipoisson and interaction terms non sig
flowDNAvsCount=glm(SockeyeTotalCount~Q_corr_qpcr + Q_corr_qpcr.lead + Avg_Temp, data=dd.qpcr.env.adults.rm, family="quasipoisson")
summary(flowDNAvsCount)
# quasipoisson and temp term non sig

par(mfrow=c(1,1))
plot(dd.qpcr.env.adults.rm$Date,dd.qpcr.env.adults.rm$SockeyeTotalCount,type='l', ylim = c(0, 900), main = "Q_corr_qpcr + Q_corr_qpcr.lead")
lines(dd.qpcr.env.adults.rm$Date[1:37],exp(predict(flowDNAvsCount)),lty=2,col="black")
lines(dd.qpcr.env.adults.rm$Date[1:37],dd.qpcr.env.adults.rm$Q_cfs[1:37],lty=3,col="blue")
lines(dd.qpcr.env.adults.rm$Date[1:37],10*dd.qpcr.env.adults.rm$Avg_Temp[1:37],lty=3,col="red")

acf(resid(flowDNAvsCount))
# residuals are not autocorrelated

```

more deviance explained with Q_corr_qpcr + Q_corr_qpcr.lead than with Q_corr_qpcr alone, but the visual fit looks better with Q_corr_qpcr alone (no major overprediction of counts)

```{r sockeye count as predictor and Q_corr_qpcr as response}
#count_t vs DNA
CountvsDNA=lm(Q_corr_qpcr[1:36] ~ SockeyeTotalCount[1:36]+SockeyeTotalCount[2:37],data=dd.qpcr.env.adults.rm)
summary(CountvsDNA)
plot(dd.qpcr.env.adults.rm$Date[2:47], dd.qpcr.env.adults.rm$Q_corr_qpcr[2:47],type='l')
predict(CountvsDNA)
lines(dd.qpcr.env.adults.rm$Date[1:36],predict(CountvsDNA),lty=2,col="blue")
acf(resid(CountvsDNA))

#add AR1 term
mdl1.ac <- gls(SockeyeTotalCount ~ Qty_ng_per_ul_mean*Q_cfs, data=dd.qpcr.env.adults.rm,
              correlation = corAR1(form=~Qty_ng_per_ul_mean))
plot(dd.qpcr.env.adults.rm$Date,dd.qpcr.env.adults.rm$SockeyeTotalCount,type='l')
lines(dd.qpcr.env.adults.rm$Date,predict(mdl1.ac),lty=2,col="blue")


#DNA*flow with lag vs count 
DNAvsCountlag=lm(SockeyeTotalCount[2:47]~Qty_ng_per_ul_mean[1:46]*Q_cfs[1:46]+Qty_ng_per_ul_mean[2:47]*Q_cfs[2:47],data=dd.qpcr.env.adults.rm)
summary(DNAvsCountlag)

plot(dd.qpcr.env.adults.rm$Date[2:47],dd.qpcr.env.adults.rm$SockeyeTotalCount[2:47],type='l')
lines(dd.qpcr.env.adults.rm$Date[2:47],predict(DNAvsCountlag),lty=2,col="blue")

acf(resid(DNAvsCount))
```




Yuanheng code


```{r explore potential independent variables}
names(dd.qpcr.env.adults.rm)
	
MyVar <- c("txtdate", "Q_corr_qpcr.rm.norm2", "Qty_ng_per_ul_mean", "Q_cfs", "SockeyeTotalCount") # date.n
	
pairs(dd.qpcr.env.adults.rm[,MyVar])
	
cor(dd.qpcr.env.adults.rm[ , c(MyVar[2:4], "date.n")])
	
corvif(dd.qpcr.env.adults.rm[ , c(MyVar[2:4], "date.n")])
	
corvif(dd.qpcr.env.adults.rm[ , c(MyVar[c(2,4)], "date.n")])
```

```{r descriptive plots}
# plot(dd.qpcr.env.adults.rm$testq_overQ, dd.qpcr.env.adults.rm$testQq)

# pdf("analysis/describe_salmon.# pdf", width = 15, height = 5)
par(las=1, mfrow = c(1,1), mar = c(2,5,2,.5), oma = c(1,1,1.5,1),cex=1.2)
# plot(dd.qpcr.env.adults.all$Date, dd.qpcr.env.adults.all$SockeyeTotalCount, xlab='', ylab='' ,type='l')
plot(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$SockeyeTotalCount, xlab='', ylab='' ,type='l')
title(ylab='Individual', outer=T, line=-1.5, cex.lab=1.2)
title(main='Daily Counts', cex.main=1.5)
	
# dev.off()
	
# pdf("analysis/describe_qpcr.# pdf", width = 15, height = 5)
par(las=1, mfrow = c(1,1), mar = c(2,5,2,.5), oma = c(1,1,1.5,1),cex=1.2)
# plot(dd.qpcr.env.adults.all$Date, dd.qpcr.env.adults.all$Q_corr_qpcr.all, xlab='', ylab='', type='l')
plot(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$Q_corr_qpcr.rm, xlab='', ylab='', type='l')
title(ylab='flow-corrected eDNA concentration', outer=T, line=-.8, cex.lab=1.2)
title(main='Daily eDNA', cex.main=1.5)

# plot(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$testQq, xlab='', ylab='', type='l')
# title(ylab='flow-corrected eDNA concentration', outer=T, line=-.8, cex.lab=1.2)
# title(main='Daily eDNA', cex.main=1.5)
# 
# plot(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$testq_overQ, xlab='', ylab='', type='l')
# title(ylab='flow-corrected eDNA concentration', outer=T, line=-.8, cex.lab=1.2)
# title(main='Daily eDNA', cex.main=1.5)

	
# dev.off()
```
	
```{r INLA models}
hist(dd.qpcr.env.adults.rm$date.n, breaks=100)
	
inla.setOption(scale.model.default = TRUE)
U = 0.1			# explore U & sigma values
hyperl=list(theta=list(prior='pc.prec', param=c(U, 0.05)))
```
	
```{r zero-inflated Poission & ar1}
# 'ar' - regularly spaced time-series
m.par0.rela = inla(SockeyeTotalCount ~ Q_corr_qpcr.rm.norm2 + f(txtdate, model = 'ar1', hyper=hyperl),
			control.compute = list(dic = T, mlik = T, cpo = T, config = T),
			control.inla = list(int.strategy = "grid", diff.logdens = 4, strategy = "laplace", npoints = 21),	
			control.predictor = list(compute = T),
			family = 'zeroinflatedpoisson1', # can be replaced by 'poisson'
			data = dd.qpcr.env.adults.rm
		)
	
summary(m.par0.rela)
```

```{r no autoregression}
m.pnt.rela = inla(SockeyeTotalCount ~ Q_corr_qpcr.rm.norm2,
			# verbose = T,
			control.compute = list(dic = T, config = T, mlik = T, cpo = T),
			control.inla = list(int.strategy = "grid", diff.logdens = 4, strategy = "laplace", npoints = 21),	
			control.predictor = list(compute = T),
			#control.family = list(list(prior = 'lognormal')),		# gamma
			family = 'zeroinflatedpoisson1', #poisson
			data = dd.qpcr.env.adults.rm
		)
	
summary(m.pnt.rela)
	
# DIC-value way too high
```

```{r model check}
#	I also tried some other model-checking criteria, but they're either too conservative (meaning all models are good according to these conservative criteria) or I'm not quite sure if I did a correct job applying them. 
#	same applies to PIT criterion, because cpo calculation failed for 32% of the data points
#	so I'm relying on the simplest ACF criterion here. 

	# PIT (probability integral transform), a form of cross-validation test 
table(m.par0.rela$cpo$failure)	# fail32% 
	
par(mfrow=c(2,1))
hist(m.par0.rela$cpo$pit, breaks=50)	# the model has bias, even though cpo fails at 32%
hist(m.par0.rela$cpo$cpo, breaks=50)	#
par(mfrow=c(1,1))	

# pdf("analysis/PIT_ar-zero.# pdf", width = 7, height = 7)

par(las=1, mfrow = c(1,1), mar = c(2,5,2,.5), oma = c(1,1,1,1),cex=1.2)
hist(m.par0.rela$cpo$pit,breaks=50, main="", cex.lab=1.2)
title(main='PIT-values, fail32%', cex.main=1.35)
	
# dev.off()
	
#  acf (auto-correlation function), checking residual correlation
resid.count.ar0 = dd.qpcr.env.adults.rm$SockeyeTotalCount - m.par0.rela$summary.fitted.values$mean
	
# pdf("analysis/acf_ar-zero.# pdf", width = 7, height = 7)

par(las = 1, mfrow = c(1,1), mar = c(4,4,2.5,.5), oma = c(2,1,.5,1),cex=1.2)
acf(resid.count.ar0, type = 'correlation', main = '', cex.lab = 1.2) # covariance
title(main = 'Residual Autocorrelation', cex.main = 1.35)
# not great at the highest peak, but I would say okay

# dev.off()

# file does not exist
# acf(resid.count.rw1, type='correlation' )
	
	# for other models 
resid.count.nt = dd.qpcr.env.adults.rm$SockeyeTotalCount - m.pnt.rela$summary.fitted.values$mean
acf(resid.count.nt,type='correlation' )
```

```{r plot model parameters with autoregression}
# ... plot latent
# pdf("analysis/time-smoother_ar-zero.# pdf", width = 10, height = 7)

par(las=1, mfrow = c(1,1), mar = c(4,3,2.5,.5), oma = c(1,1,1,1), cex=1.2)
plot(dd.qpcr.env.adults.rm$Date, m.par0.rela$summary.random$txtdate[,2][7:108], type = 'l', ylab = '', xlab = '', ylim = c(min(m.par0.rela$summary.random$txtdate[,4]), max(m.par0.rela$summary.random$txtdate[,6])))		#
	
title(ylab = 'smoother', outer = T, line = -1.4, cex.lab = 1.2)
title(main = 'Time Autoregression', cex.main = 1.5)
	
lines(dd.qpcr.env.adults.rm$Date, m.par0.rela$summary.random$txtdate[,4][7:108], lty = 2, col = 'black')
lines(dd.qpcr.env.adults.rm$Date, m.par0.rela$summary.random$txtdate[,6][7:108], lty = 2, col = 'black')
abline(h = 0, lty = 3)
	
# dev.off()
	

# .. plot fitted with autoregression m.par0.rela
# pdf("analysis/fitted_ar-zero.# pdf", width = 15, height = 5)

par(las=1, mfrow = c(1,1), mar = c(4,4,2,.5), oma = c(1,1,1,1),cex=1.2)
	
plot(dd.qpcr.env.adults.rm$Date, m.par0.rela$summary.fitted.values[,"mean"], type='n', lty=1, pch=4,col='blue', ylim=c(min(m.par0.rela$summary.fitted.values[,3]),max(m.par0.rela$summary.fitted.values[,5])), xlab='', ylab='')	#, 
title(ylab='Individual', outer=T, line=-1.2, cex.lab=1.2)
title(main='Model fit', cex.main=1.5)
	
# But we also may not want an opaque polygon
polygon.x <- c(dd.qpcr.env.adults.rm$Date, rev(dd.qpcr.env.adults.rm$Date))
polygon.y <- c(m.par0.rela$summary.fitted.values$'0.025quant', rev(m.par0.rela$summary.fitted.values$'0.975quant'))
polygon(x = polygon.x, y = polygon.y, col = 'lightblue', border = NA)
	
lines(dd.qpcr.env.adults.rm$Date, m.par0.rela$summary.fitted.values[,"mean"], lty = 1,col = 'blue')
	
points(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$SockeyeTotalCount, ylab = 'Total count',xlab = 'Date', type = 'p', pch = 20, col = '#FFA50088', lty=1)	#lwd=3, 
	
legend('topright', legend=c('count', 'fitted', '95% CI'), pch = c(20,NA, NA), col = c('#FFA50088', 'blue', 'lightblue'), lty = c(NA, 1, 1), lwd = c(1,1,10), bty = 'n', cex = 1.2)
	
# dev.off()

```

```{r plot model parameters without autoregression}

# .. plot fitted without autoregression:  m.pnt.rela
# pdf("analysis/fitted_ar-zero_no_autoregression.# pdf", width = 15, height = 5)

par(las=1, mfrow = c(1,1), mar = c(4,4,2,.5), oma = c(1,1,1,1),cex=1.2)
	
plot(dd.qpcr.env.adults.rm$Date, m.pnt.rela$summary.fitted.values[,"mean"], type='n', lty=1, pch=4,col='blue', ylim=c(min(m.pnt.rela$summary.fitted.values[,3]),max(m.pnt.rela$summary.fitted.values[,5])), xlab='', ylab='')	#, 
title(ylab='Individual', outer=T, line=-1.2, cex.lab=1.2)
title(main='Model fit', cex.main=1.5)
	
# But we also may not want an opaque polygon
polygon.x <- c(dd.qpcr.env.adults.rm$Date, rev(dd.qpcr.env.adults.rm$Date))
polygon.y <- c(m.pnt.rela$summary.fitted.values$'0.025quant', rev(m.pnt.rela$summary.fitted.values$'0.975quant'))
polygon(x = polygon.x, y = polygon.y, col = 'lightblue', border = NA)
	
lines(dd.qpcr.env.adults.rm$Date, m.pnt.rela$summary.fitted.values[,"mean"], lty = 1,col = 'blue')
	
points(dd.qpcr.env.adults.rm$Date, dd.qpcr.env.adults.rm$SockeyeTotalCount, ylab = 'Total count',xlab = 'Date', type = 'p', pch = 20, col = '#FFA50088', lty=1)	#lwd=3, 
	
legend('topright', legend=c('count', 'fitted', '95% CI'), pch = c(20,NA, NA), col = c('#FFA50088', 'blue', 'lightblue'), lty = c(NA, 1, 1), lwd = c(1,1,10), bty = 'n', cex = 1.2)
	
# dev.off()
	
	
# ... posterior distribution
# pdf("analysis/posterior_ar-zero_no_autoregression.# pdf", width = 12, height = 6)

par(las=1, mfrow = c(1,2), mar = c(4,4,1.5,.5), oma = c(1,1,1,1),cex=1.1)
	
aa = sd(dd.qpcr.env.adults.rm$Q_corr_qpcr.rm)
bb = mean(dd.qpcr.env.adults.rm$Q_corr_qpcr.rm)
	
plot(m.pnt.rela$marginals.fixed$"(Intercept)",type='l', xlab='Intercept', ylab='', cex.lab=1.2)
abline(v = m.pnt.rela$summary.fixed['(Intercept)', "0.5quant"], col = "red",lty=3)
abline(v = m.pnt.rela$summary.fixed['(Intercept)', "0.025quant"], col = "red",lty=3)
abline(v = m.pnt.rela$summary.fixed['(Intercept)', "0.975quant"], col = "red",lty=3)
plot(m.pnt.rela$marginals.fixed$"Q_corr_qpcr.rm.norm2"[,1]*aa + bb, m.pnt.rela$marginals.fixed$"Q_corr_qpcr.rm.norm2"[,2],type='l', xlab='eDNA concentration', ylab='', cex.lab=1.2)
	
abline(v = m.pnt.rela$summary.fixed['Q_corr_qpcr.rm.norm2', "0.5quant"]*aa + bb, col = "red",lty=3)
abline(v = m.pnt.rela$summary.fixed['Q_corr_qpcr.rm.norm2', "0.025quant"]*aa + bb, col = "red",lty=3)
abline(v = m.pnt.rela$summary.fixed['Q_corr_qpcr.rm.norm2', "0.975quant"]*aa + bb, col = "red",lty=3)
	
# dev.off()
```











